What makes listeners infer teaching intentions?

### 2022-02-02 paper/manuscript.Rmd
added dfs for correlation analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

### Tempo (IOIs)
Performance tempi (IOIs) were significantly correlated with participants' judgments as teaching for both techniques (Articulation; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_art$p.value))}`, Dynamics; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn$p.value))}`, *Figure \ref{fig:ioi-1}*). Participants tended to identify slower performances as teaching.

However, the Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (*p* `r if(ioi_dyn_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_dyn_norm_performance$p.value))}`). Therefore, a Spearman's rank correlation coefficient was additionally used to assess the relationship between performance tempi of dynamics recordings and participants' judgments. The result failed to reach significance (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn_spearman$estimate))`, *p* `r if(cor_ioi_dyn_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn_spearman$p.value))}`), suggesting that we need to be careful about the interpretation of the relationship between performance tempi of dynamics recordings and participants' judgments as teaching.

@@

### Articulation (KOT)
For articulation recordings, there was a significant relationship between KOT values and participants' judgments as teaching (*Figure \ref{fig:kot-1}*, left). Specifically, performances with shorter staccato (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_sta$estimate))`, *p* `r if(cor_kot_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_sta$p.value))}`) and longer legato (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_leg$estimate))`, *p* `r if(cor_kot_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_leg$p.value))}`) were more likely to be judged as teaching.

For dynamics recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Forte; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for$estimate))`, *p* `r if(cor_kot_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_for$p.value))}`, Piano; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia$estimate))`, *p* `r if(cor_kot_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_pia$p.value))}`, *Figure \ref{fig:kot-1}*, right).

The Shapiro-Wilk normality test revealed that the distribution of KOT for dynamics recordings was not normally distributed (Forte; *p* `r if(kot_for_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', kot_for_norm_performance$p.value))}`, Piano; *p* `r if(kot_pia_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', kot_pia_norm_performance$p.value))}`). Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values and participants' judgments as teaching (Forte; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for_spearman$estimate))`, *p* `r if(cor_kot_for_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_for_spearman$p.value))}`, Piano; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia_spearman$estimate))`, *p* `r if(cor_kot_pia_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_pia_spearman$p.value))}`).

@@

### Dynamics (KV)
For dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (*Figure \ref{fig:vel-1}*, right). Specifically, performances with louder forte were more likely to be judged as teaching (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for$estimate))`, *p* `r if(cor_vel_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_for$p.value))}`). However, there was no significant relationship between KV values for piano and participants' judgments as teaching (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_pia$p.value))}`).

For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg$estimate))`, *p* `r if(cor_vel_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_leg$p.value))}`, Staccato; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_sta$estimate))`, *p* `r if(cor_vel_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_sta$p.value))}`, *Figure \ref{fig:vel-1}*, left).

The Shapiro-Wilk normality test revealed that the distribution of KOT for articulation recordings for legato was not normally distributed (;*p* `r if(vel_leg_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_leg_norm_performance$p.value))}`). A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg_spearman$estimate))`, *p* `r if(cor_vel_leg_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_leg_spearman$p.value))}`).

@@

### Dynamics contrast (KV-Diff)
For dynamics recordings, there was a significant relationship between KV difference between forte and piano and participants' judgments as teaching (*Figure \ref{fig:vel-diff-1}*, right). Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop$estimate))`, *p* `r if(cor_vel_diff_ftop$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop$p.value))}`, From Piano to Forte; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof$estimate))`, *p* `r if(cor_vel_diff_ptof$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ptof$p.value))}`).

For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos$estimate))`, *p* `r if(cor_vel_diff_ltos$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ltos$p.value))}`, From Staccato to Legato; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_stol$estimate))`, *p* `r if(cor_vel_diff_stol$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_stol$p.value))}`, *Figure \ref{fig:vel-diff-1}*, left).

The Shapiro-Wilk normality test revealed that the distribution of KV difference for articulation recordings for transition points from legato to staccato was not normally distributed (;*p* `r if(vel_diff_ltos_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ltos_norm_performance$p.value))}`). A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos_spearman$estimate))`, *p* `r if(cor_vel_diff_ltos_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_ltos_spearman$p.value))}`).

@@

### Tempo (IOIs)
Unlike Experiment 1, there was no significant relationship between performance tempi (IOIs) and participants' judgments as teaching for both techniques (Articulation; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_art$p.value))}`, Dynamics; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn$p.value))}`, *Figure \ref{fig:ioi-2}*).

The Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (*p* `r if(ioi_dyn_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_dyn_norm_performance$p.value))}`). A Spearman's rank correlation coefficient also showed that there was no significant relationship between tempi for dynamics performances and participants' judgments as teaching (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn_spearman$estimate))`, *p* `r if(cor_ioi_dyn_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn_spearman$p.value))}`).

@@

### Articulation (KOT)
Unlike Experiment 1, for articulation recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Legato; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_sta$estimate))`, *p* `r if(cor_kot_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_sta$p.value))}`, Staccato; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_leg$estimate))`, *p* `r if(cor_kot_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_leg$p.value))}`, *Figure \ref{fig:kot-2}*, left).

For dynamics recordings, there was no significant relationship between KOT values for forte and participants' judgments as teaching (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for$estimate))`, *p* `r if(cor_kot_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_for$p.value))}`). However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia$estimate))`, *p* `r if(cor_kot_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_pia$p.value))}`), suggesting that performances with louder staccato were more likely to be considered as teaching performance (*Figure \ref{fig:kot-2}*, right).

@@

### Dynamics (KV)
As Experiment 1, for dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (*Figure \ref{fig:vel-2}*, right). Specifically, performances with louder forte (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for$estimate))`, *p* `r if(cor_vel_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_for$p.value))}`) and softer piano (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_pia$p.value))}`) were more likely to be judged as teaching.

The Shapiro-Wilk normality test revealed that the distribution of KV values for dynamics recordings was not normally distributed (Forte; *p* `r if(vel_for_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_for_norm_performance$p.value))}`, Piano' *p* `r if(vel_pia_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_pia_norm_performance$p.value))}`). Spearman's rank correlation coefficient also confirmed that performances with louder forte (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for_spearman$estimate))`, *p* `r if(cor_vel_for_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_for_spearman$p.value))}`) and softer piano (*r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_pia_spearman$p.value))}`) were more likely to be judged as teaching.

For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg$estimate))`, *p* `r if(cor_vel_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_leg$p.value))}`, Staccato; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_sta$estimate))`, *p* `r if(cor_vel_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_sta$p.value))}`, *Figure \ref{fig:vel-2}*, left).

@@

### Dynamics contrast (KV-Diff)
As Experiment 1, for dynamics recordings, there was a significant relationship between KV difference between forte and piano and participants' judgments as teaching (*Figure \ref{fig:vel-diff-2}*, right). Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop$estimate))`, *p* `r if(cor_vel_diff_ftop$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop$p.value))}`, From Piano to Forte; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof$estimate))`, *p* `r if(cor_vel_diff_ptof$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ptof$p.value))}`).

The Shapiro-Wilk normality test revealed that the distribution of KV-Diff values for dynamics recordings was not normally distributed (Forte to Piano; *p* `r if(vel_diff_ftop_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ftop_norm_performance$p.value))}`, Piano to Forte; *p* `r if(vel_diff_ptof_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ptof_norm_performance$p.value))}`). Spearman's rank correlation coefficient also confirmed that performances with larger contrasts between forte and piano were more likely to be judged as teaching (Forte to Piano; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop_spearman$estimate))`, *p* `r if(cor_vel_diff_ftop_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop_spearman$p.value))}`, Piano to Forte; *r* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof$estimate))`, *p* `r if(cor_vel_diff_ptof_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_ptof_spearman$p.value))}`).

>>>>

### Tempo (IOIs)
Performance tempi (IOIs) were significantly correlated with participants' judgments as teaching for both techniques (Articulation; *r(`r cor_ioi_art$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_art$p.value))}`, Dynamics; *r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn$p.value))}`, *Figure \ref{fig:ioi-1}*). Participants tended to identify slower performances as teaching.

However, the Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (*p* `r if(ioi_dyn_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_dyn_norm_performance$p.value))}`). Therefore, a Spearman's rank correlation coefficient was additionally used to assess the relationship between performance tempi of dynamics recordings and participants' judgments. The result failed to reach significance (*r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn_spearman$estimate))`, *p* `r if(cor_ioi_dyn_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn_spearman$p.value))}`), suggesting that we need to be careful about the interpretation of the relationship between performance tempi of dynamics recordings and participants' judgments as teaching.

@@

### Articulation (KOT)
For articulation recordings, there was a significant relationship between KOT values and participants' judgments as teaching (*Figure \ref{fig:kot-1}*, left). Specifically, performances with shorter staccato (*r(`r cor_kot_sta$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_sta$estimate))`, *p* `r if(cor_kot_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_sta$p.value))}`) and longer legato (*r(`r cor_kot_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_leg$estimate))`, *p* `r if(cor_kot_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_leg$p.value))}`) were more likely to be judged as teaching.

For dynamics recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Forte; *r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for$estimate))`, *p* `r if(cor_kot_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_for$p.value))}`, Piano; *r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia$estimate))`, *p* `r if(cor_kot_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_pia$p.value))}`, *Figure \ref{fig:kot-1}*, right).

The Shapiro-Wilk normality test revealed that the distribution of KOT for dynamics recordings was not normally distributed (Forte; *p* `r if(kot_for_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', kot_for_norm_performance$p.value))}`, Piano; *p* `r if(kot_pia_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', kot_pia_norm_performance$p.value))}`). Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values and participants' judgments as teaching (Forte; *r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for_spearman$estimate))`, *p* `r if(cor_kot_for_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_for_spearman$p.value))}`, Piano; *r(`r cor_kot_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia_spearman$estimate))`, *p* `r if(cor_kot_pia_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_pia_spearman$p.value))}`).

@@

### Dynamics (KV)
For dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (*Figure \ref{fig:vel-1}*, right). Specifically, performances with louder forte were more likely to be judged as teaching (*r(`r cor_vel_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for$estimate))`, *p* `r if(cor_vel_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_for$p.value))}`). However, there was no significant relationship between KV values for piano and participants' judgments as teaching (*r(`r cor_vel_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_pia$p.value))}`).

For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; *r(`r cor_vel_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg$estimate))`, *p* `r if(cor_vel_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_leg$p.value))}`, Staccato; *r(`r cor_vel_sta$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_sta$estimate))`, *p* `r if(cor_vel_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_sta$p.value))}`, *Figure \ref{fig:vel-1}*, left).

The Shapiro-Wilk normality test revealed that the distribution of KOT for articulation recordings for legato was not normally distributed (;*p* `r if(vel_leg_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_leg_norm_performance$p.value))}`). A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (*r(`r cor_vel_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg_spearman$estimate))`, *p* `r if(cor_vel_leg_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_leg_spearman$p.value))}`).

@@

### Dynamics contrast (KV-Diff)
For dynamics recordings, there was a significant relationship between KV difference between forte and piano and participants' judgments as teaching (*Figure \ref{fig:vel-diff-1}*, right). Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; *r(`r cor_vel_diff_ftop$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop$estimate))`, *p* `r if(cor_vel_diff_ftop$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop$p.value))}`, From Piano to Forte; *r(`r cor_vel_diff_ptof$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof$estimate))`, *p* `r if(cor_vel_diff_ptof$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ptof$p.value))}`).

For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; *r(`r cor_vel_diff_ltos$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos$estimate))`, *p* `r if(cor_vel_diff_ltos$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ltos$p.value))}`, From Staccato to Legato; *r(`r cor_vel_diff_stol$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_stol$estimate))`, *p* `r if(cor_vel_diff_stol$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_stol$p.value))}`, *Figure \ref{fig:vel-diff-1}*, left).

The Shapiro-Wilk normality test revealed that the distribution of KV difference for articulation recordings for transition points from legato to staccato was not normally distributed (;*p* `r if(vel_diff_ltos_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ltos_norm_performance$p.value))}`). A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (*r(`r cor_vel_diff_ltos$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ltos_spearman$estimate))`, *p* `r if(cor_vel_diff_ltos_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_ltos_spearman$p.value))}`).

@@

### Tempo (IOIs)
Unlike Experiment 1, there was no significant relationship between performance tempi (IOIs) and participants' judgments as teaching for both techniques (Articulation; *r(`r cor_ioi_art$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_art$p.value))}`, Dynamics; *r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn$p.value))}`, *Figure \ref{fig:ioi-2}*).

The Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (*p* `r if(ioi_dyn_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_dyn_norm_performance$p.value))}`). A Spearman's rank correlation coefficient also showed that there was no significant relationship between tempi for dynamics performances and participants' judgments as teaching (*r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn_spearman$estimate))`, *p* `r if(cor_ioi_dyn_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_ioi_dyn_spearman$p.value))}`).

@@

### Articulation (KOT)
Unlike Experiment 1, for articulation recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Legato; *r(`r cor_kot_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_leg$estimate))`, *p* `r if(cor_kot_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_sta$p.value))}`, Staccato; *r(`r cor_kot_sta$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_sta$estimate))`, *p* `r if(cor_kot_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_kot_sta$p.value))}`, *Figure \ref{fig:kot-2}*, left).

For dynamics recordings, there was no significant relationship between KOT values for forte and participants' judgments as teaching (*r(`r cor_kot_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_for$estimate))`, *p* `r if(cor_kot_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_for$p.value))}`). However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (*r(`r cor_kot_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_kot_pia$estimate))`, *p* `r if(cor_kot_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_kot_pia$p.value))}`), suggesting that performances with louder staccato were more likely to be considered as teaching performance (*Figure \ref{fig:kot-2}*, right).

@@

### Dynamics (KV)
As Experiment 1, for dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (*Figure \ref{fig:vel-2}*, right). Specifically, performances with louder forte (*r(`r cor_vel_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for$estimate))`, *p* `r if(cor_vel_for$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_for$p.value))}`) and softer piano (*r(`r cor_vel_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_pia$p.value))}`) were more likely to be judged as teaching.

The Shapiro-Wilk normality test revealed that the distribution of KV values for dynamics recordings was not normally distributed (Forte; *p* `r if(vel_for_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_for_norm_performance$p.value))}`, Piano' *p* `r if(vel_pia_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_pia_norm_performance$p.value))}`). Spearman's rank correlation coefficient also confirmed that performances with louder forte (*r(`r cor_vel_for$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_for_spearman$estimate))`, *p* `r if(cor_vel_for_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_for_spearman$p.value))}`) and softer piano (*r(`r cor_vel_pia$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_pia$estimate))`, *p* `r if(cor_vel_pia_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_pia_spearman$p.value))}`) were more likely to be judged as teaching.

For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; *r(`r cor_vel_leg$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_leg$estimate))`, *p* `r if(cor_vel_leg$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_leg$p.value))}`, Staccato; *r(`r cor_vel_sta$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_sta$estimate))`, *p* `r if(cor_vel_sta$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_sta$p.value))}`, *Figure \ref{fig:vel-2}*, left).

@@

### Dynamics contrast (KV-Diff)
As Experiment 1, for dynamics recordings, there was a significant relationship between KV difference between forte and piano and participants' judgments as teaching (*Figure \ref{fig:vel-diff-2}*, right). Specifically, performances with larger contrasts between forte and piano were more likely to be judged as teaching (From Forte to Piano; *r(`r cor_vel_diff_ftop$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop$estimate))`, *p* `r if(cor_vel_diff_ftop$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop$p.value))}`, From Piano to Forte; *r(`r cor_vel_diff_ptof$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof$estimate))`, *p* `r if(cor_vel_diff_ptof$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ptof$p.value))}`).

The Shapiro-Wilk normality test revealed that the distribution of KV-Diff values for dynamics recordings was not normally distributed (Forte to Piano; *p* `r if(vel_diff_ftop_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ftop_norm_performance$p.value))}`, Piano to Forte; *p* `r if(vel_diff_ptof_norm_performance$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_ptof_norm_performance$p.value))}`). Spearman's rank correlation coefficient also confirmed that performances with larger contrasts between forte and piano were more likely to be judged as teaching (Forte to Piano; *r(`r cor_vel_diff_ftop$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ftop_spearman$estimate))`, *p* `r if(cor_vel_diff_ftop_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', cor_vel_diff_ftop_spearman$p.value))}`, Piano to Forte; *r(`r cor_vel_diff_ptof$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_vel_diff_ptof$estimate))`, *p* `r if(cor_vel_diff_ptof_spearman$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.2f', cor_vel_diff_ptof_spearman$p.value))}`).
